Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 SupportingInformation.Rmd
commented the table:asym_npa results which could produce error: no sure

knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Results for tests of whether asymmetry of tail dependence was significant
                              compared to a normal-copula null hypothesis.",
             caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more)
                      than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ 
                      or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail         
                      dependence.\\label{tab_stat_npa_asym}")%>%
             kable_styling()%>%
             group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
             group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
             group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
             group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
             group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
             group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
             group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
             group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

>>>>

#knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
#             format = "latex",linesep = "",escape=F,
#             caption.short = "Results for tests of whether asymmetry of tail dependence was significant
#                              compared to a normal-copula null hypothesis.",
#             caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more)
#                      than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ 
#                      or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail         
#                      dependence.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```
